\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-19 experience.tex
removed two comments towards getting a final draft

Azure Service Fabric\footnote{\url{azure.microsoft.com/campaigns/service-fabric/}} (or Fabric for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
\PTComment{Re-added the detail here so we can discuss the bug below:}
One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries 
%by sending them \emph{replication requests}.
so that all replicas eventually have the same state. 
If the primary fails,
% (e.g.\ if the node on which the primary is running crashes), 
Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive 
%a full or partial copy (depending on whether persistent storage is used) 
a copy
of the state of the new primary in order to ``catch up'' with the other secondaries. 
%Fabric provides a name-resolution service so that clients can always find the current primary.
%The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
User-written Fabric services are complex asynchronous and distributed applications, and are thus challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

@@

\PTComment{Changed this para; added detail about the bug: }
\psharp's systematic testing was very helpful in debugging the model itself.
% Without systematic testing, we feel even catching bugs in the model 
% would have been difficult.
In order to perform systematic testing on our model,
we wrote a simple service in \psharp{}
that runs on our Fabric model.
%made up of a single machine
% and executed it on the Fabric model,
% thus yielding a pure \psharp{} system.
We tested a scenario where the primary replica
fails at some non-deterministic point
within the execution.
One such bug that we found
involved
the primary replica
failing
when a secondary replica
was about to receive a copy of the state;
the secondary was then elected to be the new primary
and yet, because the secondary stopped waiting for
a copy of the state, it was
also promoted to be an \emph{active} secondary
(one that has caught up with the other secondaries).
This caused an assertion failure in our model
allowing us to detect and fix this incorrect behaviour.

>>>>

Azure Service Fabric\footnote{\url{azure.microsoft.com/campaigns/service-fabric/}} (or Fabric for short) is a platform and API for creating reliable services that execute on a cluster of machines. 
%The developer writes a service that receives requests (e.g.\ from some client program via HTTP requests) and mutates its state based on these requests. 
In order to make the user-written service \emph{reliable}, Fabric launches several \emph{replicas} (copies) of the service, where each replica runs as a separate process on a different node in the cluster.
%\PTComment{Cut: description of primary and secondaries, and electing a new primary.}
One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries 
%by sending them \emph{replication requests}.
so that all replicas eventually have the same state. 
If the primary fails,
% (e.g.\ if the node on which the primary is running crashes), 
Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive 
%a full or partial copy (depending on whether persistent storage is used) 
a copy
of the state of the new primary in order to ``catch up'' with the other secondaries. 
%Fabric provides a name-resolution service so that clients can always find the current primary.
%The state of the service is replicated from the \emph{primary} replica to the other \emph{secondary} replicas for redundancy.
User-written Fabric services are complex asynchronous and distributed applications, and are thus challenging to test.
% They are interesting targets for systematic testing with \psharp{}.

@@

\psharp's systematic testing was very helpful in debugging the model itself.
% Without systematic testing, we feel even catching bugs in the model 
% would have been difficult.
In order to perform systematic testing on our model,
we wrote a simple service in \psharp{}
that runs on our Fabric model.
%made up of a single machine
% and executed it on the Fabric model,
% thus yielding a pure \psharp{} system.
We tested a scenario where the primary replica
fails at some non-deterministic point
within the execution.
One such bug that we found
involved
the primary replica
failing
when a secondary replica
was about to receive a copy of the state;
the secondary was then elected to be the new primary
and yet, because the secondary stopped waiting for
a copy of the state, it was
also promoted to be an \emph{active} secondary
(one that has caught up with the other secondaries).
This caused an assertion failure in our model
allowing us to detect and fix this incorrect behaviour.
